Digital History in Finland, 1488-1828

### 2016-07-10 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

>>>>

[Swedish Age of Freedom and Abolishment of Censorship 2/3]

### Number of publishers in Stockholm 1760-1770

```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
sel.places = c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
sel.years = c(1760, 1780)
pics <- list()

  # PUBLISHER COUNT
  n = sapply(split(dfs$publisher, dfs$publication_year), function (x) {
         length(unique(na.omit(x)))})
  df = data.frame(year = names(n), n = unname(n))
  if (nrow(df) > 1) {
    p = ggplot(df, aes(x = year, y = n)) +
        geom_bar(stat = "identity") +
       ggtitle(paste("Publishers:", catalogue, place)) +
       scale_x_discrete(breaks = seq(min(sel.years), max(sel.years), 10))
  } else {
    p <- ggplot() + ggtitle("Insufficient data")
  }
  pics[[paste(place, catalogue, sep = "-")]] <- p
}
}

grid.arrange(pics[[2]], pics[[4]],
             pics[[6]], pics[[8]], pics[[10]], nrow = 2)

# Remove the pics to save memory
rm(pics)	     
```
---
